Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-18 paper/paper.tex
Add more information in the related work section

%TODO: modify here
Strengthening the argument that readability matters considerably in bug report 
quality is the work of Hooimeijer et. al \cite{hooimeijer2007modeling}. They ran an analysis over
27000 bug reports from the Mozilla Firefox project, looking at self-reported 
severity, readability, daily load, submitter reputation and changes over time. 
After running the evaluation, they not only found out about the importance of
readability in bug reports, but also that attachment and comment counts are 
valuable for faster triaging and that patch count, for example, does not
contribute in the same manner as the previous two.

%TODO: modify here
Another research that agrees that stack traces are helpful in solving bug
reports faster is the one performed by Schroter et. al \cite{schroter2010stack}. They conducted
the whole experiment on the Eclipse project. They first extracted the stack
traces using the infoZilla tool(\cite{bettenburg2008extracting}), followed by
linking the stack traces to changes in the source code (change logs) by mining
the version repository of the Eclipse project. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame, with 40\% being fixed in exactly the first
stack frame.

%TODO: modify here
Other interesting findings regarding the quality of a software project's tickets
are the ones elicited in \cite{bettenburg2008duplicate}. The authors examined
whether duplicate bug reports are actually harmful to a project or they add 
quality. They collected big amount of data from the Eclipse project and ran
various kind of textual and statistical analysis on the data to find answers.
They reached the conclusion that bug duplicates contain information that is not
present in the master reports. This additional data can be helpful for developers
and it can also aid automated triaging techniques.

>>>>

Another research paper that strenghtens the argument that readability is a quality 
factor in software tickets is the one presented by Hooimeijer et. al \cite{hooimeijer2007modeling}.
They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
investigating readability, daily load, submitter reputation, the whole changelog histories 
and severity. They conclude that not only readability in the textual fields of a ticket
influence the \emph{Time-To-Close}, but also that the presence of attachments and 
the number of comments have a clear effect on the duration of triaging. On the 
other hand, the patch count and other similar fields did not provide significant 
value to the quality of tickets.

However, there are other types on information typically included in software tickets 
which might prove beneficial for developers and subsequently improve the ticket quality.
One such type is stack traces and Schroter et. al \cite{schroter2010stack} analyse how 
quickly tickets are closed when they either have stack traces included in their fields 
(e.g. description) or not. They collected their data from the Eclipse project using 
the InfoZilla tool proposed by Bettenburg et. al \cite{bettenburg2008extracting}.
Then, they linked the stack traces to changes in source code by mining the Eclipse version 
controlled repository. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame. Moreover, more than 40\% of the tickets having stack traces
got fixed in the first stack frame.

Other interesting findings regarding the quality of a software project's tickets
are the ones elicited in the study of Bettenburg et. al \cite{bettenburg2008duplicate}. The authors examined
whether duplicate bug reports are actually harmful to a project or they add 
quality. They collected big amount of data from the Eclipse project and ran
various kind of textual and statistical analysis on the data to find answers.
They reached the conclusion that bug duplicates contain information that is not
present in the master reports. This additional data can be helpful for developers
and it can also aid automated triaging techniques.
